---
title: "Rqbase"
author: "Michael Eubanks"
date: "April 28, 2016"
output: slidy_presentation
---

## Goal and Purpose
- Use an example to demonstrate on how package creation can faciliate an efficient programming work flow
- Pack scripts into functions which can be easily used in other scripts and analysis
- Stand on the shoulders of giants.

## Quickbase use cases

- Data capture tool
- Can easily scale to multiple users editing the same data: replace excel for data capture
- Low cost alternative to hiring Database administrator for small companies
- Redcap?

## Quickbase limitations

- Users create the applications
- Users create data validation and integrity rules
- Returns data in an XML format through the API
- Expensive with large data sets

## Installation
```{r eval=FALSE, warning=FALSE}
library(devtools)
install_github("mre011/Rqbase", force = TRUE)
```

## Quickbase User setup
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(XML)
library(httr)

library(dplyr)
library(tidyr)
```
Free Trial Account
```{r, warning=FALSE}
library(Rqbase)

URL <- "https://visresolutions.quickbase.com/"
username <- "meubanks@visresolutions.com"
password <- "rusergroup11"
qb_app_token <- "df7d5tacdupjsycqyjuww27z29f"
```

## Create a handle to send an authentication ticket request
```{r warning=FALSE, message=FALSE}
print(auth_ticket_handle)

```

```{r warning=FALSE, message=FALSE}
ticket_handle <-
  auth_ticket_handle(URL = URL,
                     username = username,
                     password = password)
ticket_handle
```

## Get an authentication ticket with handle
```{r warning=FALSE, message=FALSE}
auth_ticket

my_ticket <-
auth_ticket(ticket_handle)

auth_ticket_handle(URL = URL,
                   username = username,
                   password = password) %>%
  auth_ticket()

```

## Retrieve list of db_ids

```{r warning=FALSE, message=FALSE}
my_dbs <- db_ids(URL = URL, qb_ticket_id = my_ticket)
my_dbs
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
my_dbs <- 
  separate(my_dbs, col = dbname, into = "dbname", sep = ":")
```

```{r warning=FALSE, message=FALSE}
my_dbs_ls <- my_dbs$dbid
names(my_dbs_ls) <- my_dbs$dbname
my_dbs_ls
```

## Get quickbase app data into R
```{r warning=FALSE, message=FALSE}
my_dbs_ls[1]
qb_app_token
iris_response <- qb_do_query(URL = URL,
            qb_ticket_id = my_ticket,
            db_id = my_dbs_ls[2],
            app_token = qb_app_token)
```

## Return many tables
```{r warning=FALSE, message=FALSE}

lapply(my_dbs_ls, qb_do_query, 
       URL = URL,
       qb_ticket_id = my_ticket, 
       app_token = qb_app_token)
```

## Parse html response and convert content to a dataframe
```{r warning=FALSE, message=FALSE}
qb_parse(iris_response) %>%
  head()

```

## Return all apps with functional
```{r warning=FALSE, message=FALSE}
lapply(my_dbs_ls, function(x) {
  qb_do_query(db_id = x, 
       URL = URL,
       qb_ticket_id = my_ticket, 
       app_token = qb_app_token) %>%
    qb_parse() %>%
    str()
}) 
```

## Future Developments:
- POST request to create new apps from dataframes in R
- Modify existing apps
- Monitor and add users
- Automate everything